Data 621---HW1---Regression Model---Version 2

### 2020-09-09 HW1/RegModel_Adler.Rmd
Looks complete for now

### Predictions
We will use the stepwise-pairwise model to predict `TARGET_WINS` for the
separately provided evaluation set.

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r testTrain, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
```{r plotScaled, echo=TRUE, eval=FALSE}
```
```{r boxCox, echo=TRUE, eval=FALSE}
```
```{r reScale, echo=TRUE, eval=FALSE}
```
```{r reImputeThenScale, echo=TRUE, eval=FALSE}
```
```{r lm, echo=TRUE, eval=FALSE}
```
```{r nullOutput, echo=TRUE, eval=FALSE}
```
```{r satOutput, echo=TRUE, eval=FALSE}
```
```{r stepOutput, echo=TRUE, eval=FALSE}
```
```{r residPlots, echo=TRUE, eval=FALSE}
```
```{r buildTestSet, echo=TRUE, eval=FALSE}
```

>>>>

### Predictions
We will use the stepwise-pairwise model to predict `TARGET_WINS` for the
separately provided evaluation set by following the same preprocessing used for
the training and testing sets.

```{r predictions}
MBT <- fread('./data/moneyball-evaluation-data.csv')
MBT[, `:=`(TEAM_BATTING_HBP = NULL)]
MBTlng <- melt(MBT, id.vars = 'INDEX', variable.name = 'Metric',
               value.name = 'Value', variable.factor = FALSE)
MBTlng[, Value := as.double(Value)]
MBTlng <- BCL[MBTlng, on = 'Metric']
MBTlng[!is.na(Lambda), Value := BxCox(Value, Lambda)]
MBTlng[, Lambda := NULL]
MBTlngSC <- copy(MBTlng)

# Remove infinities
MBTlngSC[, Value := ifelse(is.infinite(Value), NA, Value)]

# Impute, Center, and Scale
MBTlngSC[, Value := replace(Value, is.na(Value), mean(Value, na.rm = TRUE)),
       keyby = Metric]
MBTlngSC[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
MBTSC <- dcast(MBTlngSC, INDEX ~ Metric, value.var = 'Value')
predictions <- predict(stepModel, MBTSC)
predictions
```

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r testTrain, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
```{r plotScaled, echo=TRUE, eval=FALSE}
```
```{r boxCox, echo=TRUE, eval=FALSE}
```
```{r reScale, echo=TRUE, eval=FALSE}
```
```{r reImputeThenScale, echo=TRUE, eval=FALSE}
```
```{r lm, echo=TRUE, eval=FALSE}
```
```{r nullOutput, echo=TRUE, eval=FALSE}
```
```{r satOutput, echo=TRUE, eval=FALSE}
```
```{r stepOutput, echo=TRUE, eval=FALSE}
```
```{r residPlots, echo=TRUE, eval=FALSE}
```
```{r buildTestSet, echo=TRUE, eval=FALSE}
```
```{r predictions, echo=TRUE, eval=FALSE}
```
